Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-08-29 manuscript/manuscript.Rmd
Updated code availability.

Location- and scale-invariant power transformations are implemented in the `power.transform` package. This manuscript was created using R Markdown, and is available from [https://github.com/alexzwanenburg/power.transform].

>>>>

Location- and scale-invariant power transformations are implemented in the `power.transform` package for R, and is available from [https://github.com/oncoray/power.transform] and the CRAN repository. The manuscript was created using R Markdown and is also available from the power.transform GitHub repository.
